---
title: "NIRS2019"
author: "Gude & Georgevici"
date: "30 12 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

## Clean the environmend
clean.it <- function() {
  basic.packages <- c("package:stats","package:graphics",
                      "package:grDevices","package:utils",
                      "package:datasets","package:methods",
                      "package:base")
  package.list <- dplyr::setdiff( search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)] , basic.packages)
  if (length(package.list)>0)  for(package in package.list) detach(package, character.only=TRUE)
  ll <- dplyr::setdiff( ls(envir = globalenv()), ## objects to exclude from cleaning
                        c("clean.it")) 
  rm(list = ll, envir = globalenv()); gc() # or sessionInfo()
  if(!require(pacman))install.packages("pacman")
  pacman::p_load(tidyverse,magrittr,stringi,readxl,fs,
                 chron,lubridate,tsibble,zoo, here)
}
clean.it() # clean the environment and unload and reload the libraries

# not-in-list function
"%ni%" <- Negate("%in%")

```

## Uninterpolated raw data, without patient 58 (the baseline was not documented)



```{r import raw data}



```







# The NIRS data without interpolation 




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the `r 2+3` code chunk to prevent printing of the R code that generated the plot.

```{r include = FALSE}

# colorFunc <- "heat.colors"
colorFunc <- "terrain.colors"
# colorFunc <- "topo.colors"
# colorFunc <- "cm.colors"
# colorFunc <- "rainbow"
```

Base R comes with many functions for generating colors. The code below demonstrates the `r colorFunc` function. 

## `r colorFunc`

```{r fig.cap = "The Maunga Whau volcano.", echo = FALSE}
image(volcano, col = get(colorFunc)(200))


```

This project contains the materials for lesson 7 of the [R Markdown tutorial](https://rmarkdown.rstudio.com/lesson-7.html). To begin the lesson, press the play button at the top right of the code chunk below. Then refer to the viewer pane.


